Lawvere-Tierney Sheafification in Homotopy Type Theory

### 2016-04-08 paper/paper_lipics.tex
foo

\begin{defi}
  Let $f:X \to Y$ be a map. The kernel pair $T_f$ of $f$ is the higher inductive type given
  by
  \begin{itemize}
  \item $t:~X \to T_f$
  \item $\alpha:~\forall a\,b:X,~f(a) = f(b) \to t(a) = t(b)$
  \item $\alpha_1:~\forall a:X,~\alpha(a, a, 1) = 1$
  \end{itemize}
  We view $T_f$ as the coequalizer of
  $\xymatrix{
    \sum_{a,b:X} f(a) = f(b) \dar[r]{4pt}^-{\pi_1}_-{\pi_2} & X
  }$
  preserving the identity.
  We call $\tilde f$ the map $T_f \to Y$ given by induction.
\end{defi}

Then, the considered diagram $C(f)$  is the mapping telescope of the iterations
of $T$.
\begin{defi}
  Let $f$ be a map from $X$ to $Y$. Then the iterated kernel pair of
  $f$ $C(f)$
  is given by the diagram
  $\xymatrix{
    C(f) := X \ar[r]^-t & T_f \ar[r]^-t & T_{\tilde f} \ar[r] &\cdots
  }$
\end{defi}

@@

In section~\ref{ssec:overview}, we announce that sheafification can be
seen a translation of type theories\footnote{We define the translation on Martin-Löf type theory,
  but it could also be done for CIC as well.}, as it has been done for
forcing~\cite{jaber2012extending}. Actually, this is not a specific
property of sheafification, but something shared by all modalities. We
hence don't explicit it in the paper, but we do in this appendix.

>>>>

\begin{defi}
  Let $f:X \to Y$ be a map. The coequalizer $T_f$ of the kernel pair of $f$ is the higher inductive type given
  by
  \begin{itemize}
  \item $t:~X \to T_f$
  \item $\alpha:~\forall a\,b:X,~f(a) = f(b) \to t(a) = t(b)$
  \item $\alpha_1:~\forall a:X,~\alpha(a, a, 1) = 1$
  \end{itemize}
  We view $T_f$ as the coequalizer of
  $\xymatrix{
    \sum_{a,b:X} f(a) = f(b) \dar[r]{4pt}^-{\pi_1}_-{\pi_2} & X
  }$
  preserving the identity.
  We call $\tilde f$ the map $T_f \to Y$ given by induction.
\end{defi}

Then, the considered diagram $C(f)$  is the mapping telescope of the iterations
of $T$.
\begin{defi}
  Let $f$ be a map from $X$ to $Y$. Then the {\em iterated kernel pair} of
  $f$ 
  is given by the diagram
  $\xymatrix{
    C(f) := X \ar[r]^-t & T_f \ar[r]^-t & T_{\tilde f} \ar[r] &\cdots
  }$
\end{defi}

@@

In section~\ref{ssec:overview}, we announce that sheafification can be
seen a translation of type theories\footnote{We define the translation on Martin-Löf type theory,
  but it could also be done for CIC as well.}, as it has been done for
forcing~\cite{jaber2012extending}. Actually, this is not a specific
property of sheafification, but something shared by all modalities. We
hence don't explicit it in the paper, but only here in this appendix.
